---
title: "YouGov"
output:
  html_notebook:
    toc: true
    toc_float: true
    toc_depth: 2
    theme: spacelab
    code_folding: hide
---

Even though the Democratic primary field has started to coalesce around formerly left policies such as Medicare for All, most candidates are still unwilling to hold strong  positions on a variety of historically taboo labor, gun, and Israel-US topics. 

YouGov has conducted a survey of nationally representative 2018 voters about such issues. (Un)surprisingly, the American public does not view these topics as controversial as Twitter pundits would have you believe. 

A full 64% of respondents support "red flag" laws, which allow courts to temporarily remove firearms from the homes of individuals who are deemed to pose a violent risk to themselves or others. 

Similarly, a plurality of respondents support a four-day work week (38.5%) and oppose laws that forbid boycotts of Israel (33.7%). 

On their face, these policies are controversial nonstarters; in reality, they enjoy broad-based support.

```{r, echo=FALSE, include=FALSE}
source("explore.R")
```

```{r}
g_bar
```

```{r}
g_likert
```

